# Section 2: Absentee / Vote by Mail

## Q2.1: How many contests did you vote in on your 2020 ballot?

```{r}

Q2.1_data <- df %>%
  drop_na(Q2.1) %>% 
  group_by(Q2.1) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.1) %>% 
  mutate(response = as_factor(response)) %>% 
  mutate(response = fct_relevel(response, "All of the contests", "Nearly all of the contests", "Most of the contests", "About half of the contests", "Just a few contests")) %>% 
  mutate(id = as.numeric(response)) %>%
  select(id, everything())

freq_table(Q2.1_data)

```

## Q2.2: Why did you request an absentee ballot? Please select all that apply.

```{r}

Q2.2_data <- df %>%
  filter(if_any(Q2.2_absent:Q2.2_other, ~ !is.na(.x))) %>% 
  pivot_longer(Q2.2_absent:Q2.2_other, names_to = "response") %>%
  drop_na(value) %>% 
  group_by(response) %>% 
  tally() %>% 
  mutate(percent = n/sum(n))

freq_table_unsorted(Q2.2_data)

```

## Q2.3: Have you voted absentee or by mail in a previous election?

```{r}

Q2.3_data <- df %>%
  drop_na(Q2.3_prevVBM) %>% 
  group_by(Q2.3_prevVBM) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.3_prevVBM)

freq_table_unsorted(Q2.3_data)

```

## Q2.4: How did you request an absentee ballot?

```{r}

Q2.4_data <- df %>%
  drop_na(Q2.4_requestMethod) %>% 
  group_by(Q2.4_requestMethod) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.4_requestMethod)

freq_table_unsorted(Q2.4_data)

```

## Q2.5: Did you log on to your voter registration record to do any of the following? Please select all that apply.

```{r}

Q2.5_data <- df %>%
  filter(if_any(Q2.5_yes_absentee_sentTime:Q2.5_no, ~ !is.na(.x))) %>% 
  pivot_longer(Q2.5_yes_absentee_sentTime:Q2.5_no, names_to = "response") %>%
  drop_na(value) %>% 
  group_by(response) %>% 
  tally() %>% 
  mutate(percent = n/sum(n))

freq_table_unsorted(Q2.5_data)

```

## Q2.6: How was your mail ballot delivered to you?

```{r}

Q2.6_data <- df %>%
  drop_na(Q2.6_deliveryMethod) %>% 
  group_by(Q2.6_deliveryMethod) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.6_deliveryMethod)

freq_table_unsorted(Q2.6_data)

```

## Q2.7: Did you fill out your ballot with anyone else, such as a family member or friend, or did you complete your ballot by yourself?

```{r}

Q2.7_data <- df %>%
  drop_na(Q2.7_ballotBuddy) %>% 
  group_by(Q2.7_ballotBuddy) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.7_ballotBuddy)

freq_table_unsorted(Q2.7_data)

```

## Q2.8: With whom did you complete your ballot? Please select all that apply.

```{r}

Q2.8_data <- df %>%
  filter(if_any(Q2.8_ballotBuddy_partner:Q2.8_ballotBuddy_unknown, ~ !is.na(.x))) %>% 
  pivot_longer(Q2.8_ballotBuddy_partner:Q2.8_ballotBuddy_unknown, names_to = "response") %>%
  drop_na(value) %>% 
  group_by(response) %>% 
  tally() %>% 
  mutate(percent = n/sum(n))

freq_table_unsorted(Q2.8_data)

```

## Q2.9: When did you return your mail ballot?

```{r}

Q2.9_data <- df %>%
  drop_na(Q2.9_returnDate) %>% 
  group_by(Q2.9_returnDate) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.9_returnDate) %>% 
  mutate(response = as_factor(response)) %>% 
  mutate(response = fct_relevel(response, "After Election Day", "On Election Day", "2-3 days before Election Day", "One week before Election Day", "2-3 weeks before Election Day", "4 or more week before Election Day")) %>% 
  mutate(id = as.numeric(response)) %>%
  select(id, everything())

freq_table(Q2.9_data)

```

## Q2.10: Who returned your ballot or dropped it in the mail? 

```{r}

Q2.10_data <- df %>%
  drop_na(Q2.10_returnPerson) %>% 
  group_by(Q2.10_returnPerson) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.10_returnPerson)

freq_table_unsorted(Q2.10_data)

```

## Q2.11: How did you return your ballot?

```{r}

Q2.11_data <- df %>%
  drop_na(Q2.11_returnMethod_voter) %>% 
  group_by(Q2.11_returnMethod_voter) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.11_returnMethod_voter)

freq_table_unsorted(Q2.11_data)

```

## Q2.12: If someone else returned your ballot, how did they return your ballot?

```{r}

Q2.12_data <- df %>%
  drop_na(Q2.12_returnMethod_someone) %>% 
  group_by(Q2.12_returnMethod_someone) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.12_returnMethod_someone)

freq_table_unsorted(Q2.12_data)

```

## Q2.13: Did you return anyone else's ballot?

```{r}

Q2.13_data <- df %>%
  drop_na(Q2.13_returnOtherBallots) %>% 
  group_by(Q2.13_returnOtherBallots) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.13_returnOtherBallots)

freq_table_unsorted(Q2.13_data)

```

## Q2.14: Whose ballot(s) did you return? Please select all that apply.

```{r}

Q2.14_data <- df %>%
  filter(if_any(Q2.14_returnOtherBallots_spouse:Q2.14_returnOtherBallots_other, ~ !is.na(.x))) %>% 
  pivot_longer(Q2.14_returnOtherBallots_spouse:Q2.14_returnOtherBallots_other, names_to = "response") %>%
  drop_na(value) %>% 
  group_by(response) %>% 
  tally() %>% 
  mutate(percent = n/sum(n))

freq_table_unsorted(Q2.14_data)

```


## Q2.16: Why did you decide to drop off your ballot rather than mail the ballot back in? Please select all that apply.

```{r}

Q2.16_data <- df %>%
  filter(if_any(Q2.16_returnDropoffReason_convenience:Q2.16_returnDropoffReason_other, ~ !is.na(.x))) %>% 
  pivot_longer(Q2.16_returnDropoffReason_convenience:Q2.16_returnDropoffReason_other, names_to = "response") %>%
  drop_na(value) %>% 
  group_by(response) %>% 
  tally() %>% 
  mutate(percent = n/sum(n))

freq_table_unsorted(Q2.16_data)

```

## Q2.17: Were you contacted by your local election official because there was a problem with your ballot and it could not be counted? 

```{r}

Q2.17_data <- df %>%
  drop_na(Q2.17_contactedByElectionOfficial) %>% 
  group_by(Q2.17_contactedByElectionOfficial) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.17_contactedByElectionOfficial)

freq_table_unsorted(Q2.17_data)

```

## Q2.18: Were you able to resolve the problem?

```{r}

Q2.18_data <- df %>%
  drop_na(Q2.18_resolveProblem) %>% 
  group_by(Q2.18_resolveProblem) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.18_resolveProblem)

freq_table_unsorted(Q2.18_data)

```

## Q2.20: Did you check to see if your ballot arrived at your County Elections office before Election Day?

```{r}

Q2.20_data <- df %>%
  drop_na(Q2.20_checkArrival) %>% 
  group_by(Q2.20_checkArrival) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.20_checkArrival)

freq_table_unsorted(Q2.20_data)

```

## Q2.21: Overall, how difficult was it to follow all the instructions necessary to cast your ballot and return it to be counted?

```{r}

Q2.21_data <- df %>%
  drop_na(Q2.21_instructionQuality) %>% 
  group_by(Q2.21_instructionQuality) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.21_instructionQuality) %>% 
  mutate(response = as_factor(response)) %>% 
  mutate(response = fct_relevel(response, "Very easy", "Somewhat easy", "Somewhat hard", "Very hard")) %>% 
  mutate(id = as.numeric(response)) %>%
  select(id, everything())

freq_table(Q2.21_data)

```

## Q2.22: How concerned were you that your ballot would arrive at the County Clerk’s office in time to be counted?

```{r}

Q2.22_data <- df %>%
  drop_na(Q2.22_returnConcern) %>% 
  group_by(Q2.22_returnConcern) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.22_returnConcern) %>% 
  mutate(response = as_factor(response)) %>% 
  mutate(response = fct_relevel(response, "Very concerned", "Somewhat concerned", "Not too concerned", "Not at all concerned")) %>% 
  mutate(id = as.numeric(response)) %>%
  select(id, everything())

freq_table(Q2.22_data)

```

## Q2.23: Did you encounter any problems marking or completing your ballot that may have interfered with your ability to cast your vote as intended?

```{r}

Q2.23_data <- df %>%
  drop_na(Q2.23_interferingProblems) %>% 
  group_by(Q2.23_interferingProblems) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.23_interferingProblems)

freq_table_unsorted(Q2.23_data)

```

## Q2.25: Given your experience this year with mail in voting, how likely are you to vote absentee next time?

```{r}

Q2.25_data <- df %>%
  drop_na(Q2.25_voteVBMAgain) %>% 
  group_by(Q2.25_voteVBMAgain) %>% 
  tally() %>% 
  mutate(percent = n/sum(n)) %>%
  rename(response = Q2.25_voteVBMAgain) %>% 
  mutate(response = as_factor(response)) %>% 
  mutate(response = fct_relevel(response, "Very likely", "Somewhat likely", "Not too likely", "Not at all likely")) %>% 
  mutate(id = as.numeric(response)) %>%
  select(id, everything())

freq_table(Q2.25_data)

```